When are Fuzzy Extractors Possible?

### 2014-08-11 info-bounds/FuzzyExtPossibility.tex
adding min max and starting on hardness of dist agnostic sketching

\title{When are Fuzzy Extractors Possible?}

@@

\bnote{connection to obfuscation}
\section{Preliminaries}
\label{sec:preliminaries}
For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote by $X = X_1,..., X_\ell$  the tuple $(X_1,\dots, X_\ell)$.  For a set of indices $J$, $X_{J}$ is the restriction of $X$ to the indices in $J$.  The set $J^c$ is the complement of $J$.  The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$,
and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.   For a random variable $W$, let $H_0(W)$ be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.
The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
For a distinguisher $D$ we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$ (we extend it to a class of distinguishers $\mathcal{D}$ by taking the maximum over all distinguishers $D\in\mathcal{D}$).  We denote by $\mathcal{D}_{s}$ the class of randomized circuits which output a single bit and have size at most $s$.

@@

\begin{definition}
\label{def:fuzzy min-ent}
A distribution $W$ in a metric space $(\mathcal{M}, \dis)$ has $(t, k)$-fuzzy min-entropy, denoted $\Hfuzz(W) \ge k$ if the following holds:
\[
\forall m\in \mathcal{M},  \sum_{w\in W | \dis(w, m)\le t} Pr[W=w] \leq 2^{-k}.
\]
\end{definition}

@@

\begin{definition}
Let $W$ denote a distribution.  A secure sketch, $(\sketch_W, \rec_W)$ is called \emph{distribution-aware} if the correctness and security properties hold for the distribution $W$.  That is, 
\begin{enumerate}
\item \emph{Correctness} For all $w\in W$ and for all $w'\in\mathcal{M}$,  if $\dis(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta$ where the probability is taken over the coins of $\sketch$ and $\rec$.  If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.
\item \emph{Security} $W$ is unknown conditioned on $s$: $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
\end{definition}
Note that correctness is only required to hold for points in the support of the distribution $W$, the algorithms are allowed the description of $W$ and security need only hold for the distribution $W$.  When we consider distribution-aware algorithms, we generally assume they are \emph{inefficient}, this seems inherent to make use of the (possibly)~exponential size distributions.  It is not clear how to meaningfully define efficient distribution aware algorithms.  If the algorithms were required to be efficient, they could only encode a negligible portion of the probability space of $W$, and would have to ``work'' on all distributions $W'$ with the same probability mass function on the encoded space.  This would make the algorithms a distribution-oblivious fuzzy extractor for all distributions with this property.

@@

\begin{table}
\begin{tabular}{l | l | c}
Lower bounds & Distribution-Dependent & Distribution-Oblivious\\
\hline
Well-spread distribution & $\Hfuzz(W)$ & $\log |B_t|$\\
Flat distribution & $\Hfuzz(W) - \log (1/\delta)$ &$\log |B_t|$\\
Arbitrary distribution & $\Hfuzz(W) - \log (1/\delta) - \log \log \mathcal{M}$ & $\log |B_t|$
\end{tabular}
\caption{Residual entropy of secure sketches for complete recovery.}
\label{tab:upper bounds}
\end{table}
\bnote{Fix right side of table}
\bnote{the table should move.}
%We begin with the left column of Table~\ref{tab:upper bounds} and provide constructions of sketches~(which generalize to fuzzy extractors).  We then show that building distribution-agnostic secure sketches and fuzzy extractors is significantly harder.

\section{Distribution-Dependent Sketches}
In this section, we consider show it is possible to build distribution-aware fuzzy extractors and secure sketches whenever $\Hfuzz(W)= \omega(\log n)$.
We consider increasingly complex types of distributions and end with an arbitrary distribution over a metric space.  We construct secure sketches but all constructions can be transformed to fuzzy extractors using \lemref{lem:fuzzy ext construction}.  In the next section \bnote{what section?} we consider distribution-oblivious algorithms.

@@

\bnote{stopped here}
\subsection{Flat distributions}
In the previous section we showed that info-theoretically it is easy to produce a secure sketch and fuzzy extractor for a well-spread distribution when the algorithms are allowed to encode the input distribution $W$.  
%\lemref{lem:nosketchwellspread} showed that if a fuzzy extractor~(resp. secure sketch) is built for a particular well-spread distribution, it is not necessary to write down information-reconciliation information.  
In this section, we consider information-theoretic bounds on distributions that contain multiple points in each ball.  
We begin by considering flat distributions where the probability of each point in $W$ is the same.

@@

Recall that fuzzy min-entropy is a lower bound of the adversaries success probability for any scheme (\defref{def:fuzzy min-ent}).  Fuzzy min-entropy is total weight of the maximum probability ball.  For flat distribution, this is directly correlated to the ball with the largest number of points.  That is, for a flat distribution 
\begin{align*}
\Hfuzz(W) &= -\log \max_{w^* \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w^*)\le t\} * \Pr[W=w]\\
&= -\log \max_{w^* \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w^*)\le t\} *2^{-\Hoo(W)}\\
&=\Hoo(W) -\log \max_{w^* \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w^*)\le t\} 
\end{align*}
For notational convenience, we denote the ball with the largest number of points as $B_{t, max}$.  For any scheme, the adversary's success probability is 
\begin{align}
\Hfuzz(W) = \Hoo(W) -\log |B_{t, max}|.\label{eq:fuzz for flat}
\end{align}
%We start by considering distributions that have a fixed number of neighbors for each point.
%
%\begin{definition}
%We call a distribution $W$, over metric space $\mathcal{M}$, $(c, t)$-\emph{fixed neighbor} if there exists a constant $c$ such that for all points in $x\in \mathcal{M}$ there are exactly $c$ points $w\in W$ such that $\dis(w, x)\le t$.  We say that $W$ is a $(c, t)$-\emph{bounded neighbor distribution} if for all point $x\in\mathcal{M}$ there are at most $c$ points $w\in W$ such that $\dis(w, x)\le t$.
%\end{definition}
%
%\textbf{Note:} A fixed neighbor distribution is a special case of a bounded-neighbor distribution.
We now present an information-theoretic construction for flat distributions.  We first introduce the notion of a pairwise-independent hash:

@@

We now show a sufficiently-long universal hash function suffices to construct an information-theoretic fuzzy extractor.

@@

We now argue correctness.  Fix some $w, w'$.  Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$ recall that the size of $W^*$ is at most $B_{t, max}$ and since $w, w'$ are chosen independently of $\sketch$ this set is independent of the choice of $\mathcal{K}$.  Note $\rec$ will never output $\perp$ as the correct $w$ will match the hash, our goal is to bound the probability that another element $w^*$ collides, that is $F(K, w^*) = F(K, w)$.
\begin{align*}
\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
 &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R|} = \frac{|B_{t, max}|-1}{|R|}
\end{align*}
Where the inequality proceeds by union bound, the first equality proceeds by the universality of $F$, and the second equality proceeds by noting the number of neighbors is bounded by $|B_{t, max}|$.  This completes the proof.
\end{proof}
\begin{corollary}
Let $n$ be a security parameter.  
If $|R| \ge |B_{t, max}|* n^{\omega(1)}$ then \consref{cons:pairwise hash} is correct with overwhelming probability.  That is, setting $\log |R| = \log |B_{t, max}| + \omega(\log n)$ suffices.
\end{corollary}

Note that \consref{cons:pairwise hash} writes down essentially the worst case number of bits in all setting, it knows the maximum number of points in any ball and writes down that number~(with an additional super-logarithmic factor to prevent collisions).  Recall, our hope is to find a sketch that achieves total security equal to the fuzzy min-entropy of the distribution.  Thus, the remaining entropy for this construction is 
\[
\Hav(W |\sketch(W)) = \Hoo(W) - \log |B_{t, max}| - \omega(\log n)
\]
For a flat distribution this is within a super-logarithmic factor of optimal~(see Equation~\eqref{eq:fuzz for flat}).  Intuitively, this is because the sketch is deconflicting for the ball with the largest number of points.  For a flat distribution, this is also the ball with the largest total weight.  We will see this becomes more difficult as we move to the setting where points have very different probability.  In this setting, we may write down a large number of bits to deal with a low weight ball that has a large number of points, but this may completely reveal the high weight balls. We will compensate for this problem by writing down a variable number of bits.
%with a fixed number of neighbors, 
%\begin{align*}
%\Hfuzz(W) &= -\log \max_{x\in \mathcal{M}}, \sum_{w | \dis(w, x)\le t} \Pr[W=w]\\
%&=-\log \max_{x\in \mathcal{M}}, -\log \sum_{w | \dis(w, x)\le t} 2^{-\Hoo(W)}\\
%&= -\log c2^{-\Hoo(W)} = \Hoo(W) - \log c
%\end{align*}
%Thus, the construction is optimal up to a super-logarithmic factor for flat sources with a fixed number of neighbors.  We now attempt to remove both of these restrictions.

@@

Dealing with non-flat distributions requires a new strategy.  Ideally, this strategy should be aware of the density of the current ball and aware that when an original reading comes from a sparse ball it is not necessary to write down many bits.  We first consider a mechanism that tries to reduce the arbitrary case to the flat case by selecting a candidate flat distribution.  Unfortunately, this mechanism does not work as a distribution with high fuzzy min-entropy can be formed as a convex combination of distributions with almost no fuzzy min-entropy~(\secref{sec:convex comb}).

We then show a solution that comes within a super-logarithmic factor of optimal of optimal by partitioning the probability space~(\secref{sec:layered hash}).

\subsubsection{Leveraging convex combinations?}
\label{sec:convex comb}
In many situations solving a problem for min-entropy distributions can be reduced to solving the problem for flat distributions and then using the fact that any min-entropy distribution is a convex combination of flat distributions.  For example, consider the following hypothetical extension to \consref{cons:pairwise hash}.  Let $W$ be some distribution that is a finite convex combination of flat sources $W_1,..., W_n$ where each $\forall i, \Hoo(W_i)\ge k$.\footnote{A distribution may be an  convex combination of an infinite number of distributions.  However, the difficulty arises even when considering a finite combination so we restrict ourselves to this simpler case.}  For convenience we assume that the coefficients on all $W_i$ are the same and distributions may be repeated.

>>>>

\newcommand{\Succ}{\mathsf{Succ}}
\newcommand{\Adv}{\mathbf{Adv}}
 \newcommand{\Exp}{\mathbf{Exp}}

\title{When are Fuzzy Extractors Possible?}
\author{Benjamin Fuller\footnote{Boston University and MIT Lincoln Laboratory. Email: {\tt bfuller@cs.bu.edu}.}~~~~~~~~~~Leonid Reyzin\footnote{Boston University.  Email: {\tt reyzin@cs.bu.edu}.}~~~~~~~~~~Adam Smith\footnote{Pennsylvania State University. Work done in part while the author was at Boston University and Harvard University.  Email: {\tt asmith@psu.edu}.  }}

@@

\bnote{connection to obfuscation}
\section{Preliminaries}
\label{sec:preliminaries}
\bnote{be careful with overloading of $\ell$, both key length and number of levels.}
For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote by $X = X_1,..., X_\ell$  the tuple $(X_1,\dots, X_\ell)$.  For a set of indices $J$, $X_{J}$ is the restriction of $X$ to the indices in $J$.  The set $J^c$ is the complement of $J$.  The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$,
and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.   For a random variable $W$, let $H_0(W)$ be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.
The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
For a distinguisher $D$ we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$ (we extend it to a class of distinguishers $\mathcal{D}$ by taking the maximum over all distinguishers $D\in\mathcal{D}$).  We denote by $\mathcal{D}_{s}$ the class of randomized circuits which output a single bit and have size at most $s$.

@@

\begin{definition}
\label{def:fuzzy min-ent}
A distribution $W$ in a metric space $(\mathcal{M}, \dis)$ has $(t, k)$-fuzzy min-entropy, denoted $\Hfuzz(W) \ge k$ if the following holds:
\[
\forall m\in \mathcal{M},  \sum_{w\in W | \dis(w, m)\le t} \Pr[W=w] \leq 2^{-k}.
\]
\end{definition}

@@

\begin{definition}
Let $W$ denote a distribution.  A secure sketch, $(\sketch_W, \rec_W)$ is called \emph{distribution-aware} if the correctness and security properties hold for the distribution $W$.  That is, 
\begin{enumerate}
\item \emph{Correctness} For all $w\in W$ and for all $w'\in\mathcal{M}$,  if $\dis(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta$ where the probability is taken over the coins of $\sketch$ and $\rec$.  If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.  Note correctness is guaranteed only for the support of $W$.
\item \emph{Security} The distribution $W$ is unknown conditioned on $s$: $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
\end{definition}
Note that correctness is only required to hold for points in the support of the distribution $W$, the algorithms are allowed the description of $W$ and security need only hold for the distribution $W$.  When we consider distribution-aware algorithms, we generally assume they are \emph{inefficient}, this seems inherent to make use of the (possibly)~exponential size distributions.  It is not clear how to meaningfully define efficient distribution aware algorithms.  If the algorithms were required to be efficient, they could only encode a negligible portion of the probability space of $W$, and would have to ``work'' on all distributions $W'$ with the same probability mass function on the encoded space.  This would make the algorithms a distribution-oblivious fuzzy extractor for all distributions with this property.

@@

\begin{table}
\begin{tabular}{l | l | c}
Lower bounds & Distribution-Dependent & Distribution-Oblivious\\
\hline
Well-spread distribution & $\Hfuzz(W)$ & $\log |B_t|$\\
Flat distribution & $\Hfuzz(W) - \log (1/\delta)$ &$\log |B_t|$\\
Arbitrary distribution & $\Hfuzz(W) - \log (1/\delta) - \log \log \mathcal{M}- O(1)$ & $\log |B_t|$
\end{tabular}
\caption{Residual entropy of secure sketches for complete recovery.}
\label{tab:upper bounds}
\end{table}
\bnote{Fix right side of table}
\bnote{the table should move.}
%We begin with the left column of Table~\ref{tab:upper bounds} and provide constructions of sketches~(which generalize to fuzzy extractors).  We then show that building distribution-agnostic secure sketches and fuzzy extractors is significantly harder.

\section{Distribution-Dependent Sketches}
In this section, we consider show it is possible to build distribution-aware fuzzy extractors and secure sketches whenever $\Hfuzz(W)= \omega(\log n)$.
We consider increasingly complex types of distributions and end with an arbitrary distribution over a metric space.  We construct secure sketches but our constructions can be transformed to fuzzy extractors using \lemref{lem:fuzzy ext construction}.  In \secref{sec:dist oblivious} we consider distribution-oblivious algorithms.

@@

\subsection{Flat distributions}
In the previous section we showed it is easy to produce secure sketch for well-spread distributions in the distribution aware setting.
%\lemref{lem:nosketchwellspread} showed that if a fuzzy extractor~(resp. secure sketch) is built for a particular well-spread distribution, it is not necessary to write down information-reconciliation information.  
In this section, we consider distributions with multiple points in each ball where points have the same probability.

@@

Recall that fuzzy min-entropy is a lower bound of the adversaries success probability for any scheme.  Fuzzy min-entropy is total weight of the maximum probability ball~(\defref{def:fuzzy min-ent}).  For flat distributions, this is proportional to the largest number of points in any ball.  More precisely, 
\begin{align*}
\Hfuzz(W) &= -\log \left(\max_{w^* \in \mathcal{M}} \left| \{w | w\in W \wedge \dis(w, w^*)\le t\} \right|* \Pr[W=w]\right) \\
&= -\log\left( \max_{w^* \in \mathcal{M}} |\{w | w\in W \wedge \dis(w, w^*)\le t\}| *2^{-\Hoo(W)}\right) \\
&=\Hoo(W) -\log\left( \max_{w^* \in \mathcal{M}}| \{w | w\in W \wedge \dis(w, w^*)\le t\} |\right)
\end{align*}
For notational convenience, we denote the ball with the largest number of points as $B_{t, max}$.  For any scheme, the adversary's success probability is 
\begin{align}
\Hfuzz(W) = \Hoo(W) -\log |B_{t, max}|.\label{eq:fuzz for flat}
\end{align}
%We start by considering distributions that have a fixed number of neighbors for each point.
%
%\begin{definition}
%We call a distribution $W$, over metric space $\mathcal{M}$, $(c, t)$-\emph{fixed neighbor} if there exists a constant $c$ such that for all points in $x\in \mathcal{M}$ there are exactly $c$ points $w\in W$ such that $\dis(w, x)\le t$.  We say that $W$ is a $(c, t)$-\emph{bounded neighbor distribution} if for all point $x\in\mathcal{M}$ there are at most $c$ points $w\in W$ such that $\dis(w, x)\le t$.
%\end{definition}
%
%\textbf{Note:} A fixed neighbor distribution is a special case of a bounded-neighbor distribution.
We now present a construction for flat distributions.  We use pairwise-independent hashes:

@@

We now show a sufficiently-long universal hash function suffices to construct an information-theoretic fuzzy extractor.  The work of Skoric et al.~\cite{skoric2009efficient} use universal hash functions in the setting where there are a polynomial number of possible error patterns.

@@

We now argue correctness.  Fix some $w, w'$.  Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$ recall that the size of $W^*$ is at most $B_{t, max}$ and since $w, w'$ are chosen independently of $\sketch$ this set is independent of the choice of $\mathcal{K}$.  Note $\rec$ will never output $\perp$ as the correct $w$ will match the hash, our goal is to bound the probability that another element $w^*$ collides, that is $F(K, w^*) = F(K, w)$.
\begin{align*}
\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
 &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R|} \le \frac{|B_{t, max}|-1}{|R|}
\end{align*}
Where the inequality proceeds by union bound, the first equality proceeds by the universality of $F$, and the second inequality proceeds by noting the number of neighbors is bounded by $|B_{t, max}|-1$.  This completes the proof.
\end{proof}
\begin{corollary}
Let $n$ be a security parameter.  
If $|R| \ge |B_{t, max}|* n^{\omega(1)}$ then \consref{cons:pairwise hash} is correct with overwhelming probability.  That is, setting $\log |R| = \log |B_{t, max}| + \omega(\log n)$ suffices.
\end{corollary}

Note that \consref{cons:pairwise hash} writes down essentially the worst case number of bits in all setting, it knows the maximum number of points in any ball and writes down that number~(with an additional super-logarithmic factor to prevent collisions).  Recall, our hope is to find a sketch that achieves total security equal to the fuzzy min-entropy of the distribution.  Thus, the remaining entropy for this construction is 
\[
\Hav(W |\sketch(W)) = \Hoo(W) - \log |B_{t, max}| - \omega(\log n)
\]
For a flat distribution this is within a super-logarithmic factor of optimal~(see Equation~\eqref{eq:fuzz for flat}).  Furthermore, whenever $\Hfuzz(W) = \omega(\log n)$, we can construct a secure sketch that is correct with overwhelming probability while retaining a super-logarithmic amount of entropy~(by choosing $\delta$ depending on $\Hfuzz(W)$).  That is, we can construct a secure sketch whenever there is super-logarithmic starting entropy.  Intuitively, this is because the sketch is deconflicting for the ball with the largest number of points.  For a flat distribution, this is also the ball with the largest total weight.  We will see this becomes more difficult as we move to the setting where points have very different probability.  %In this setting, we may write down a large number of bits to deal with a low weight ball that has a large number of points, but this may completely reveal the high weight balls. We will compensate for this problem by writing down a variable number of bits.
%with a fixed number of neighbors, 
%\begin{align*}
%\Hfuzz(W) &= -\log \max_{x\in \mathcal{M}}, \sum_{w | \dis(w, x)\le t} \Pr[W=w]\\
%&=-\log \max_{x\in \mathcal{M}}, -\log \sum_{w | \dis(w, x)\le t} 2^{-\Hoo(W)}\\
%&= -\log c2^{-\Hoo(W)} = \Hoo(W) - \log c
%\end{align*}
%Thus, the construction is optimal up to a super-logarithmic factor for flat sources with a fixed number of neighbors.  We now attempt to remove both of these restrictions.

@@

Dealing with non-flat distributions requires a new strategy.  Ideally, this strategy should be aware of the density of the current ball and aware that when an original reading comes from a sparse ball it is not necessary to write down many bits.  Many solutions for manipulating high entropy distributions leverage a solution for flat distributions and use the fact that high entropy distributions are convex combinations of flat distributions.  In \apref{sec:convex comb}, we show that it is difficult to exploit this property in our scenario.  The main issue is that a distribution with high fuzzy min-entropy may be formed from component distributions each of which have no fuzzy min-entropy.

As mentioned, the main obstacle in the arbitrary setting is distinguishing between a setting where a ball has a few high probability points and a large number of low probability points.
We address this by describing the probability of the point $w_0\in W$ seen in sketch.  Then the hash is applied only considering the maximum weight of the ball containing points of similar probability.  We can think of this construction as dividing the distribution $W$ into probability levels, and each component level is nearly flat.  As long as levels are large enough, they do not reveal too much information about the stored point $W$.  Naturally, there is a tradeoff between the number of levels and how useful the level information is to both the \rep algorithm and the adversary.

\noindent Before showing that \consref{cons:leveling} works, we extend our notation for the maximum likelihood ball to the leveled case.  Let $B_{t, i, max}$ be the ball that contains the most points in $L_i$.  That is,
\[
B_{t, i, max} = \max_{w^* \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w^*)\le t \wedge \Pr[W=w]\in L_i\}.
\]
\begin{theorem}
\label{thm:layered hashing}
Let $\delta>0$ be an function of $n$.  Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of pairwise independent hash functions where $|R_i| = (|B_{t, i, max}|-1) /\delta$.  Then \consref{cons:leveling} is a $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 3$.
\end{theorem}
\bnote{right now this is stated without $\ell$.  I found the expression to be really gross with $\ell$ included.  Thoughts?  I know $\ell$ needs to be there because the construction uses it.}
\begin{proof}
\textbf{Correctness:}  We begin by arguing correctness.  Let $\ell$ be a parameter describing the number of levels.\footnote{later we will set $\ell = m$ to simplify expressions and obtain the theorem statement.  The proof can be carried out for an arbitrary $\ell$.}  Fix some $w, w'$.  If $\Pr[W=w]\le 2^{-(n+\ell)}$, then $w$ is simply transmitted to $\rec$ and correctness is clear.  Now consider the case when $\Pr[W=w]> 2^{-(n+\ell)}$, let $L_i^*$ be the level of $\Pr[W=w]$.
Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$ such that $\forall w \in W^*, \Pr[W^*=w]\in L_i^*$. The size of $W^*$ is at most $B_{t, i, max}$. The choice of $w, w'$ is independent of $\sketch$, so this set is independent of $\mathcal{K}_i$~(it does effect the value of $i$ but not the particular outcome from $\mathcal{K}_i$).  Note $\rec$ will never output $\perp$ as the correct $w$ will match the hash.  The probability that another element $w^*$ is:
\begin{align*}
\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
 &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R_i|} \le \frac{|B_{t, i, max}|-1}{|R_i|} = \delta
\end{align*}
Where the inequality proceeds by union bound, the first equality proceeds by the universality of $F$, and the second inequality proceeds by noting the number of neighbors is bounded by $|B_{t, i, max}|$.

\textbf{Ideal Adversary with access to Level Information:} Before arguing security of the actual construction, we consider the optimum performance of an adversary that receives the level information.  %We first consider the optimum strategy for an adversary that receives just the information about the probability of $w$.  
An adversary that receives $i$ as input the best strategy is to guess a point that has the most nearby weight in that layer.  That is, $w^*\leftarrow A(i)$ such that $\max_{w^* \in \mathcal{M}}\Pr_{w\in W | 2^{-(i+1)}\le \Pr[W=w]\le 2^{-i}}[\dis(w, w^*)]$.The success of this adversary is at least $2^{-(i+1)}|B_{t,i, max}|$ as there at $B_{t, i, max}$ nearby points in that layer each with probability at least $2^{-(i+1)}$.  Note there are $n-m+\ell$ outcomes for $i$ so the overall success of such an adversary is at most $n-m+\ell$ better than an adversary without such input~(by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}).  That is, 
\begin{align}
\expe_{i | m\le i \le n+\ell}2^{-(i+1)}|B_{t, i, max}|&\le \expe_{i | m\le i \le n+\ell}\left( \max_{w^*\in W}\sum_{w\in W| 2^{-(i+1)}\le \Pr[W=w]\le 2^{-i} \wedge \dis(w, w^*) \le t}\Pr [W=w]\right) \label{eq:link fuzz 1}\\
&\le \left(n-m+\ell\right)\left(\max_{w^*\in W} \sum_{w\in W | \dis(w, w^*)\le t} \Pr[W=w]\right)\label{eq:link fuzz 2}\\
&= \left(n-m+\ell\right)\Hfuzz(W)\label{eq:link fuzz 3}
\end{align}
\textbf{Security:}
We now argue security.  First note that the total weight of points whose probability is less than $2^{-(n+\ell)}$ is at most $2^{-\ell}$~(there are at most $2^n$ points in the distribution).  That is, $\sum_{w | \Pr[W=w]\le 2^{-(n+\ell)}}\Pr[W = w] \le 2^{-\ell}$.  Let $1_{\text{low}}$ be the indicator random variable for $\Pr[W=w]\le 2^{-n}$.  Then 
\begin{align*}
\Hav(W | \sketch(W)) = -\log \left(\Pr[1_{\text{low}}=1] * 1 + \Pr[1_{\text{low}} =0]   2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)\\
-\log\left( 2^{-\ell} + (1-2^{-\ell})2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)
\end{align*}
For the remainder of the proof, we seek a bound on 
\[
2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0} = \max_{w\in W | \Pr[W=w]>2^{-(n+\ell)}}\Pr[W=w | \sketch(W)].
\]
We separate out this quantity into levels:
\begin{align*}
\max_{w\in W | \Pr[W=w]>2^{-(n+\ell)}}\left(\Pr[W=w | \sketch(W)]\right) &= \expe_{i | m\le i \le n+\ell} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w | \sketch(W), i]\right)\\
&= \expe_{i | m\le i \le n+\ell} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]*2^{|\sketch(W)|i|}\right)\\
&\le \expe_{i | m\le i \le n+\ell} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]*2^{H_0(\sketch(W) | i)}\right)\\
&\le \expe_{i | m\le i \le n+\ell} \left(2^{-i}*|B_{t, i, max}|/\delta\right)\\
&\le\frac{ \expe_{i | m\le i \le n+\ell} \left(2^{-(i+1)}*|B_{t, i, max}|\right)}{2\delta}\\
%&=\delta \sum_{i | m\le i \le n+\ell} \Pr[W\in L_i]\left(2^{-i}*|B_{t, i, max}|\right)
%\end{align*}
%Now consider This allows us to conclude that 
%\begin{align*}
%\max_{w\in W | \Pr[W=w]>2^{-n}\epsilon}\left(\Pr[W=w | \sketch(W)]\right) 
&= \frac{(n-m+\ell) 2^{-\Hfuzz(W)}}{2\delta}.
\end{align*}
Where the last line follows by Equations~\eqref{eq:link fuzz 1}-\eqref{eq:link fuzz 3}.
Combining both cases we have:
\begin{align*}
\Hav(W | \sketch(W)) = -\log \left(2^{-\ell}+\frac{(1-2^{-\ell})(n-m+\ell)2^{-\Hfuzz(W)}}{2\delta}\right).
\end{align*}
Setting $\ell = m$ yields
\begin{align*}
\Hav(W | \sketch(W)) &= -\log \left(m+\frac{(1-2^{-m})(n)2^{-\Hfuzz(W)}}{2\delta}\right)\\
&\ge -\log \min\{m, \frac{(1-2^{-m}) n2^{-\Hfuzz(W)}}{2\delta}\})-1\\
&\ge \Hfuzz(W) - \log n + \log \delta - \log (1-2^{-m}) - 2\\
&\ge \Hfuzz(W) - \log n + \log \delta - 3\\
\end{align*}
Where the third line follows from the second because $\Hfuzz(W)\le \Hoo(W) = m$. The last line follows from the fourth because if $m\ge 1$ then $\log (1-2^{-m})\le 1$ and if $m< 1$ the entire bound is vacuous as $\Hfuzz(W)< 1$ and thus the bound is negative.
\end{proof}

\begin{corollary}
Let $n$ be a security parameter and let $\mathcal{M} =\zo^n$.
For any distribution $W$ over $\mathcal{M}$ with $\Hfuzz(W)=\omega(\log n)$, there exists a distribution aware secure sketch with $\tilde{m} = \omega(\log n)$ residual min-entropy and overwhelming correctness.  Furthermore, there exists a $(\mathcal{M}, \Hoo(W), \ell = \omega(\log n), \epsilon)$ distribution aware fuzzy extractor with $\epsilon = \ngl(n)$) and overwhelming correctness.
\end{corollary}
\section{Distribution-Oblivious Sketches}
\label{sec:dist oblivious}

In the previous section, we saw it is possible to construct secure sketches and fuzzy extractors when the algorithms are allowed to precisely known and encode the source distribution.  This type of assumption is problematic for two reasons 1) we rarely have complete information about a distribution 2) encoding the entire source distribution made the algorithms in the previous section inherently inefficient.  In this section we ask if the results can be replicated for a family of distributions.  Example families of distributions include all well-spread distributions, all distributions of a given min-entropy, all distributions where individual symbols have entropy.  The hope is that we can leverage a construction for each member of the family~(which was shown to exist in the previous section).  Unfortunately, we show for secure sketches this is not the case.  That is, there are families of distributions~(where each member has fuzzy min-entropy) where any secure sketch must not leave enough super-logarithmic min-entropy.

\subsection{A definitional equivalence}
Before proceeding to our result, we consider the definition of a fuzzy extractor.  The standard definition requires a secure sketch to work for all members $W$ of a family $\mathcal{V}$.  This can be thought of as a two stage process: 1) the system designer specifies $(\sketch, \rec)$, 2) the adversary specifies a particular member $W\in \mathcal{V}$.  We will say the system designer wins if the adversary can guess the element in $W$ with low probability, and the adversary wins if the can recover $w\in W$ with noticeable probability.  That is, we can formulate this process as a standard cryptographic game.  Let $\mathcal{A}, \mathcal{C}$ be the adversary and challenger respectively. We will formulate this as a two player game.

\begin{center}
\begin{minipage}{1in}
\begin{tabbing}
123\=123\=123\=123\=123\=\kill
\textbf{Experiment} $\Exp^{\mathcal{V}}_1(\mathcal{A}, \mathcal{C}, k)$: \\
$(\sketch, \rec)\leftarrow \mathcal{C}(\mathcal{V})$\\
$W \leftarrow \mathcal{A}(\mathcal{V}, \sketch, \rec)$\\
If $W\not\in \mathcal{V}$ return $0$.\\
If $\Hav(W | \sketch(W))\ge k$ set reward $(1, -1)$ else reward $(-1, 1)$.
\end{tabbing} \end{minipage} 
\end{center}

%Alternatively, we can think of this as a zero sum game where the adversary wins $1$ and the challenger loses $1$ when the guess is correct with the opposite reward otherwise.
In the results that follow it will be useful to think of a different formulation of this game.  Let $\mathcal{W}$ be a distribution~(of distributions) over the family $\mathcal{V}$.

\begin{center}
\begin{minipage}{1in}
\begin{tabbing}
123\=123\=123\=123\=123\=\kill
\textbf{Experiment} $\Exp^{\mathcal{V}}_2(\mathcal{A}, \mathcal{C})$: \\
$\mathcal{W} \leftarrow \mathcal{A}(\mathcal{V})$\\
$(\sketch, \rec)\leftarrow \mathcal{C}(\mathcal{V}, \mathcal{W})$\\
$W \leftarrow \mathcal{W}$\\
If $W\not\in \mathcal{V}$ return $0$.\\
If $\Hav(W | \sketch(W))\ge k$ set reward $(1, -1)$ else reward $(-1, 1)$.
\end{tabbing} \end{minipage} 
\end{center}
